Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a). The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region. \red{(PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE (``The spatial discontinuities ... permeability region'') ... ACTUALLY THIS SENTENCE IS NOT CORRECT AS (IN THIS CASE) THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY OR IN PRESSURE, JUST A LARGE K AND P DISTRIBUTION ... IN ADDITION ...\underline{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?})}

\medskip
Numerical simulation was performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}. Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the development of wetting phase through the four subdomains, demonstrating the preferential flow path through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. \red{KOSTAS ... COULD YOU REVIEW THIS SECTION ... IT INITIALLY REFERS TO VR=1 AND THEN TO VR=10 ... BUT IT IS NOT CLEAR IF THE PLOTS IN FIG 4 REFER TO VR1 OR VR10 ...}

>>>>

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a). The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region. \red{(PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE (``The spatial discontinuities ... permeability region'') ... ACTUALLY THIS SENTENCE IS NOT CORRECT AS (IN THIS CASE) THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY OR IN PRESSURE, JUST A LARGE K AND P DISTRIBUTION ... IN ADDITION ...\underline{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?})}

A numerical simulation was also performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}. Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the development of wetting phase through the four subdomains, demonstrating the preferential flow path through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. \red{THIS PARAGRAPH ONLY MAKE SENSE IF YOU ARE SHOWING THE RESULTS OF VR =10. HOWEVER, FIGS 4b-c REFER TO VR=1, WHICH, BY THE WAY, HAS NO COMMENT IN THE PREVIOUS PARAGRAPH ... IN THIS SECTION YOU \underline{\bf MUST} TALK ABOUT CROSS-FLOW !!}
